---
output: github_document
bibliography: refs.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gvcR

<!-- badges: start -->
<!-- badges: end -->

The goal of gvcR is to ...

## Installation

The released version of `gvcR` package is accessible through devtools.

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github('warint/gvcR')
```

## How-To

### Step 1: Getting the location’s list

A user needs to enter the location of the risk. To have access to this location, the following function provides this information.

```{r, eval=FALSE}
gvcr_location() # A list of all locations will be produced

gvcr_location(location = "Canal") # A list of locations that contain the word 'Canal' will be produced

gvcr_location("Canal") # A list of locations that contain the word 'Canal' will be produced
```

### Step 2: Getting the indicator’s code

A user needs to enter the code of the desired risk. To do so, the following function provides access to all the risks of interest.

```{r, eval=FALSE}
gvcr_risk() # A list of all risks code will be produced

gvcr_risk(indicators = "attack") # The risk code will be produced for risks that contain the word 'attack'

gvcr_risk("attack") # The risk code will be produced for risks that contain the word 'attack'
```


### Step 3: Getting the data

Once the user knows the location and the risk’s code, s.he can collect the data in a very easy way through this function:

```{r, eval=FALSE}
gvcr_data(location = "Panama Canal", risks = "S-T") # It generates a data frame for 'Terrorist attack' (S-T) risk in the location 'Panama Canal'

gvcr_data("Panama Canal", "S-T") # It generates a data frame for 'Terrorist attack' (S-T) risk in the location 'Panama Canal'

gvcr_data(location = c("Panama Canal", "Suez Canal"), risks = c("S-T", "S-C")) # It generates a data frame for 'Terrorist attack' (S-T) and 'Conflict' (S-C) risks in the location 'Panama Canal'

gvcr_data(category = "Weather and climate risk") # It generates a data frame for all locations and risks in the category 'Weather and climate risk'

gvcr_data(levels = "High risk") # It generates a data frame for all locations and risks with a 'High risk'

gvcr_data() # It generates a data frame of the complete dataset
```

### Cite ‘gvcR’

If you use the `gvcR` package for research, education, policy making or other related purposes, please cite the package as well as @wellesley_chokepoints_2017. Consider making them a [donation](https://www.chathamhouse.org/support-us) to help them pursue their work.

To cite the ‘gvcR’ package in your work:

Warin, Thierry. 2021. Warint/gvcR. https://github.com/warint/gvcR.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
toBibtex(citation("gvcR"))
```

### Acknowledgements

The author would like to thank the Center for Interuniversity Research and Analysis of Organizations (CIRANO, Montreal) for its support, as well as Marine Leroi and Martin Paquette. The usual caveats apply.

### References

